High-level cognition is supported by at least second order dynamic correlations in neural activity patterns

### 2019-08-30 paper/main.tex
backing up progress, working on feature selection

\subsubsection*{Feature selection}
We sought to examine which types of neural features (i.e.,
activations, first-order dynamic correlations, and higher-order
dynamic correlations) were informative to the temporal decoders.
Using the notation above, these features correspond to $\mathbf{Y}_0$,
$\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on (we examined
up to tenth order correlations, or $\mathbf{X}_{10}$).  Separately for
each of these types of features, we \textbf{JRM STOPPED HERE}--
compute lambda, then compute optimal weighted mix using half of the
template data, then decode the to-be-decoded data using those weights.

>>>>

\subsubsection*{Feature selection and testing}
We sought to examine which types of neural features (i.e.,
activations, first-order dynamic correlations, and higher-order
dynamic correlations) were informative to the temporal decoders.
Using the notation above, these features correspond to $\mathbf{Y}_0$,
$\mathbf{X}_1$, $\mathbf{X}_2$, $\mathbf{X}_3$, and so on (we examined
up to tenth order correlations, or $\mathbf{X}_{10}$).

One challenge to fairly evaluating high-order correlations is that if
the kernel used in Equation~\ref{eqn:timecorr} is wider than a single
timepoint, each repeated application of the equation will result in
further temporal blur.  Because our primary assessment metric is
temporal decoding accuracy, this unfairly biases against detecting
meaningful signal in higher-order correlations (relative to
lower-order correlations).  We attempted to mitigate temporal blur in
estimating each $\mathbf{X}_n$ by using a Dirac $\delta$ function
kernel (which places all of its mass over a single timepoint;
Fig.~\ref{fig:kernels}b) to compute each lower-order correlation
($\mathbf{X}_1, \mathbf{X}_2, ..., \mathbf{X}_{n-1}$).  We then used a
(potentially wider, as described below) kernel to compute $\mathbf{X}_{n}$ from
$\mathbf{X}_{n-1}$.  In this way, temporal blurring was applied only in the
last step of computing $\mathbf{X}_n$.  We note that, because each
$\mathbf{X}_n$ is a low-dimensional representation of the
corresponding $\mathbf{Y}_n$, the higher-order correlations we
estimated reflect true correlations in the data with lower-fidelity
than estimates of lower-order correlations.

After computing each
$\mathbf{X}_1, \mathbf{X}_2, ..., \mathbf{X}_{n-1}$ for each
participant, we divided participants into two equally sized groups
($\pm 1$ for odd numbers of participants):
$\mathcal{G}_{\mathrm{train}}$ and $\mathcal{G}_{\mathrm{test}}$.  We
then further subdivided $\mathcal{G}_{\mathrm{train}}$ into
$\mathcal{G}_{\mathrm{train}_1}$ and $\mathcal{G}_{\mathrm{train}_2}$.
We then computed $\mathbf{\Lambda}$ temporal correlation matrices for
each type of neural feature, using $\mathcal{G}_{\mathrm{train}_1}$
and $\mathcal{G}_{\mathrm{train}_2}$.  This resulted in $n+1$
$\mathbf{\Lambda}$ matrices (one for the original timeseries of neural
activations, and one for each of $n$ orders of dynamic correlations).
Our objective was to find a set of weights of each of these
$\mathbf{\Lambda}$ matrices such that the weighted average of the
$n+1$ matrices yielded the highest decoding accuracy.  We used
quasi-Newton gradient ascent~\citep{NoceWrig06}, using decoding
accuracy as the objective function to be maximized, to find an optimal
set of training data-derived weights, $\phi_{0, 1, ..., n}$, where
$\sum_{i=0}^n \phi_i = 1$ and where
$\phi_i \geq 0 \forall i \in \left[0, 1, ..., n\right]$.

After estimating an optimal set of weights, we computed a new set of
$n + 1$ $\mathbf{\Lambda}$ matrices correlating timepoints from  $\mathcal{G}_{\mathrm{train}}$
and $\mathcal{G}_{\mathrm{test}}$.

\textbf{JRM STOPPED HERE}--
say something about delta function kernel to avoid something at higher
orders, then in the last order use a gaussian, laplace, or mexican hat kernel.

compute lambda, then compute optimal weighted mix using half of the
template data, then decode the to-be-decoded data using those weights.
